\documentclass{resume}

\usepackage[left=0.35in,top=0.3in,right=0.35in,bottom=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{array}
\usepackage[hidelinks]{hyperref}

\setlist[itemize]{noitemsep, topsep=0pt, parsep=0pt}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{CHINMAYA R}

\address{Bangalore, India \quad +91 89702 49705}

\address{
\href{mailto:chinmayar2003@gmail.com}{chinmayar2003@gmail.com} \quad
\href{https://github.com/ChinmayaR23}{github.com/ChinmayaR23} \quad
\href{https://leetcode.com/u/ChinmayaRao/}{leetcode.com/ChinmayaRao} \quad
\href{https://www.linkedin.com/in/chinmaya-r-/}{LinkedIn}
}
\begin{document}

\begin{rSection}{EDUCATION}

{\bf Bachelor of Technology in Computer Science} \hfill {2021 -- 2025} \\
PES University, Bangalore \hfill \textit{CGPA: 9.0/10.0}

\end{rSection}

\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages        & Java, C++, Go, Python, Solidity \\
Databases        & MySQL, Vertica, MongoDB \\
Cloud \& DevOps  & Docker, AWS (Basic), Git/GitHub \\
Frameworks \& Tools & Spring Boot, VS Code, OpenAI Gym, Remix IDE \\
\end{tabular}
\end{rSection}

\begin{rSection}{WORK EXPERIENCE}

\textbf{Associate Software Engineer (Backend)} \hfill {Jun 2025 -- Present} \\
\textit{Netcore Cloud} \hfill \textit{Bangalore, India}
\begin{itemize}
    \item Engineered analytical modules in Java, Python and Go for \textbf{RFM segmentation, engagement analysis and cohort analysis}, enabling marketers to derive insights from large user datasets.
    \item Wrote optimized SQL queries on \textbf{Vertica} to handle large-scale aggregations and improve report generation speed.
\end{itemize}

\textbf{Backend Intern} \hfill {Jan 2025 -- Jun 2025} \\
\textit{Netcore Cloud} \hfill \textit{Bangalore, India}
\begin{itemize}
    \item Built internal synthetic data generation tools to accelerate feature testing in lower environments and reduce QA dependency.
\end{itemize}

\end{rSection}

\begin{rSection}{RESEARCH PUBLICATIONS}

\textbf{Enhancing Efficiency in Smart Grid Billing with Blockchain Technology}
\href{https://ieeexplore.ieee.org/abstract/document/10625244}{(Paper Link)} \hfill {2024} \\
\textit{International Conference on Sustainable Computing and Smart Systems (ICSCSS)}
\begin{itemize}
    \item Authored and presented a paper proposing a decentralized smart grid billing architecture using Solidity smart contracts.
\end{itemize}

\end{rSection}

\begin{rSection}{PROJECTS}

\textbf{PathFinder — RL-based Connectivity System} $|$ \textit{Python, OpenAI Gym, PPO} \hfill {2024}
\begin{itemize}
    \item Built a \textbf{reinforcement learning} agent to determine optimal infrastructure paths balancing elevation, vegetation (NDVI) and urban constraints.
    \item Processed geospatial raster data into feature matrices to train a Proximal Policy Optimization (PPO) model.
    \item Designed the system to minimize environmental impact while maximizing connectivity efficiency between urban nodes.
\end{itemize}

\textbf{ChessTime — Real-Time Multiplayer Chess Platform} $|$ \textit{Next.js 14, Spring Boot, WebSocket, MySQL} \hfill {2025} \\
\href{https://chesstime.duckdns.org/}{Live Demo} \quad
\href{https://github.com/ChinmayaR23/chess-time}{github.com/ChinmayaR23/chess-time}
\begin{itemize}
    \item Built a full-stack real-time chess platform with live matchmaking and server-authoritative clock management using STOMP over WebSocket.
    \item Implemented JWT-based OAuth2 authentication (GitHub/Google), Elo rating system, and persistent game history.
    \item Optimized move throughput with asynchronous database writes and scalable backend architecture.
\end{itemize}

\end{rSection}

\begin{rSection}{ACADEMIC ACHIEVEMENTS}
\begin{itemize}
    \item \textbf{Prof. MRD Scholarship:} Four-time recipient for maintaining SGPA within the top 20\% at PES University.
    \item \textbf{Prof. CNR Rao Scholarship:} Two-time recipient for ranking within the top 5\% of the batch.
    \item \textbf{Code Battle Winner:} Member of the winning team (twice) at PES University coding competition.
\end{itemize}
\end{rSection}

\end{document}
